---
title: "Unit5_Application"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1)
library(gam)
library(tidyverse)
library(tidymodels)
library(knitr)

```
## Question 1 (Adapted from ISLR #6)
1. In this exercise, you will further analyze the Wage data set considered
throughout this chapter.

a. Perform polynomial regression to predict wage using age using a polynomial of order 2. 
b. Use cross-validation to select the optimal degree d for the polynomial. Use a grid between 2 and 10.
c. Make a plot of the resulting polynomial fit to the data. 


### Answer

```{r Q1}
####You can use the code in reg_splines_notes.R for tidymodels. However, you will need to adapt it to poly regs instead
###of spline regs. 
library(ISLR)
###do not do an initial split, we won't be using a true test set for this problem
folds <- vfold_cv(Wage, v = 10)

##b.
polyreg_recipe <- 
  recipe(formula = wage ~ age, data = Wage) %>% 
  step_poly(age, degree = tune("df_val"))

#####
####


#######Since you aren't using an initial split, use the following to fit to the full data and save predicted values.
final_polyreg %>% 
  fit(Wage) %>% 
  predict(Wage) %>% 
  bind_cols(Wage) -> wage_fit



```



*************************************


## Question 2 (Adapted from ISLR #9)
This question uses the variables dis (the weighted mean of distances
to five Boston employment centers) and nox (nitrogen oxides concentration in parts per 10 million) from the Boston data. We will treat dis as the predictor and nox as the response.

a. Use a natural spline regression to predict nox using dis using a spline with 2 knots. 
b. Use cross-validation to select the optimal degrees of freedom for the natural. Use a grid between 1 and 10.
c. Make a plot of the resulting natural spline to the data. 


### Answer

```{r Q2}
boston_data <- MASS::Boston
####You can use the code in reg_splines_notes.R for tidymodels. 
###do not do an initial split, we won't be using a true test set for this problem




```



*************************************

## Question 3 (Adapted from ISLR #10)

This question relates to the College data set.

a. Create a new variable called ActRate, which equals Accept/Apps.
b. Fit a smoothing spline with ActRate as a predictor and Outstate as the response with an effective df =5.
c. Refit the previous model, but use CV to find an optimal level of df.
d. Make a plot of the resulting smoothing spline to the data. 

### Answer

```{r Q3}
glimpse(College)
####
####tidymodels will not work with smoothing splines. See smooth_splines_notes for how to do this.
##### We won't be using a true test set in this case. You do not have to split the data.



```


## Question 4 (Adapted from ISLR #10)

This question relates to the College data set and the ActRate you created in Question 3.

b. Fit a GAM using a smoothing spline for ActRate and a natural spline for Grad.Rate using 3 for the paramters in both.
c. Refit several (4) other GAMs for Outstate, and calculate the MSE for each one.
d. Make a plot of the resulting GAMS to the data. 

### Answer

```{r Q4}
####
####tidymodels will not work with many GAMs.

###simple augment
gam_augment <- function(gam_mod, new_data)
{
  tibble(.fitted = predict(gam_mod, newdata = new_data)) %>% bind_cols(new_data)
}

#####add additional models here
gam_models <- tibble(models = c(
  Outstate ~ ActRate + Grad.Rate
))

gam_models %>%
  mutate(mods = map(models, ~gam::gam(.x, data = College)),
         gam_fitted = map(mods, ~gam_augment(.x, College)),
         model_text = map_chr(models, ~paste(.x[2],.x[3],sep='~'))) -> fitted_gams


####use unnest and group by model_text and use summarize to calculate the MSE.


#####in ggplot, use color = model_text in aes and the unnested data

```
